### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Rewrite Introduction with four main results

Second, birth spacing can have a substantial impact on children's outcomes.
Most of the research finds a negative impact of short spacing on child health, although 
identifying the causal mechanisms have proven more difficult
\citep{Conde-Agudelo2006,Conde-Agudelo2012}.
There are three pathways through which birth intervals can affect health.
First, there is maternal depletion, where the mother does not have sufficient time to 
recover after her last pregnancy before she becomes pregnant again.%
\footnote{
This depletion can take the form of nutrition, folate, or cervical insufficiency.
}
Second, disease transmission either from mother to child or between children.
Third, sibling competition, where siblings close in age compete for scarce resources and
parental care.
Which mechanism dominates is of particular interest when son preference drives spacing 
decisions.
Both the maternal depletion and the transmission of disease explanations predominately
affect the subsequent child and the mother.
Only sibling competition has the potential to affect the older child negatively.

@@

% [TK Results - need updating]
There are three main results.
First, there has been a general increase in the length of spacing between births
over the four decades covered by the data.
Second, the most substantial increase in spacing is for the women who
are most likely to use sex selection.
Specifically, among the best-educated women, those with no boys now has 
significantly longer spacing---and a more male-biased sex ratio---than 
similar women with boys.
Third, women with no education still follow the standard pattern of
short spacing when they have girls and little evidence of the use of sex
selection.
In other words, these women adhere to a strategy where they achieve a
son through higher fertility rather than the use of sex selection.

>>>>

Second, birth spacing can have a substantial impact on children's outcomes.
Most of the research finds a negative impact of short spacing on child health---especially 
for very short intervals of 18 months or less---although identifying the causal mechanisms 
have proven more difficult \citep{Conde-Agudelo2006,Conde-Agudelo2012}.
There are three pathways through which birth intervals can affect health.
First, there is maternal depletion, where the mother does not have sufficient time to 
recover after her last pregnancy before she becomes pregnant again.%
\footnote{
This depletion can take the form of nutrition, folate, or cervical insufficiency.
}
Second, disease transmission either from mother to child or between children.
Third, sibling competition, where siblings close in age compete for scarce resources and
parental care.
Which mechanism dominates is of particular interest when son preference drives spacing 
decisions.
Both the maternal depletion and the transmission of disease explanations predominately
affect the subsequent child and the mother.
Only sibling competition has the potential to affect the older child negatively.

@@

There are four main results.
First, there has been a general increase in the intervals between births for all education 
groups over the four decades covered by the data.
These increases are larger the higher the parity and the higher the education level.
Second, those women who are most likely to use sex selection, well-educated women with no
sons, have seen the largest increases in birth intervals.
As a result, we now have a complete reversal of the traditional spacing pattern for
well-educated women, and instead observe the longest spacing for women with no sons.
Third, women who are least likely to use sex selection, those with no education in
rural areas, still follow the standard pattern of short spacing when they have girls and 
little evidence of the use of sex selection.
In other words, these women adhere to a strategy where they achieve a son through higher 
fertility rather than the use of sex selection.
Fourth, the traditional pattern of longer average spacing when women have one or more sons
appear to arise from more very long intervals, rather than from fewer very short birth 
intervals; across education groups there appear to be little difference in the likelihood
of having a very short birth interval across sex compositions, especially for lower
parities.
